---
title: "HSV Data Table"
output: html_document
Name: Arianna Pierre
---

#Prerequisites
```{r}
library(tidyverse)
library(ggplot2)
library(pivottabler)
```

##We will explore the Health Systems Engineering Dataset:

```{r}
Original_Data <- read.csv("HSE_Data_Table.csv")
```
#Data Description 
```{r}
glimpse(Sodium_Data)
```


# Exploratory Data Analysis

## Data Summaries
```{r}
Original_Data%>%
  filter(Sodium.missing.flag == "Yes")%>%
  arrange(Age..Unit.Entry.)
```


### Sodium Data Table
```{r}
Sodium_Data <- Original_Data %>%
  select(Sodium ,Sodium.missing.flag)%>%
  mutate(Levels = case_when(
    between(Sodium, 112, 134.99) ~ "Low",
    between(Sodium, 135, 145.0) ~ "Normal",
    between(Sodium, 145.1, 163) ~ "High"))
Sodium_Data
```
## What does “missing sodium” represent – how is the data “managed”?
```{r}
Sodium_Data%>%
  filter(Sodium.missing.flag == "Yes")
```
Missing sodium means when the patient has enough sodium in their body to show they did not set off a test that could mean they are critically ill. 
```{r}

```


# Data Visualization

Create a histogram for all Sodium data points

```{r}
Sodium_Data %>%
  ggplot() + 
  geom_histogram(aes( x = Sodium), binwidth = 1) +
  labs(title = "Sodium Point (Including missing) levels in Tampa Patients")

```

# Sodium Level Histogram

```{r}
Sodium_levels <- Sodium_Data %>%
  filter(Sodium.missing.flag == "No")%>%
  ggplot() + 
  geom_histogram(aes(x = Sodium, fill = Levels), binwidth = .75)+
  labs(title=" All Available Sodium Levels in Tampa Patients", x="Sodium", y="Count")

Sodium_levels
```
- When sodium levels in the blood are *lower* than 135 meq/l, it is a condition called Hyponatremia.
- Sodium levels *between* 135 and 145meq/l are within the normal range.
- When sodium levels in the blood are *higher* than 145 meq/l, it is a condition called Hypernatremia.




