---
title: "HSV Data Table"
output: html_document
Name: Arianna Pierre, Tai Polur
---

#Introduction
Our general research topic is to determine the level of sodium in admitted patients. Throughout the data the sodium level is either flagged or not, further variables would describe the admitted patients sodium level as low, normal, or high.

#Prerequisites
```{r}
library(tidyverse)
library(ggplot2)
library(pivottabler)
```

##We will explore the Health Systems Engineering Dataset:

```{r}
Original_Data <- read.csv("HSE_Data_Table.csv")
```
#Data Description 
```{r}
glimpse(Sodium_Data)
```


# Exploratory Data Analysis

## Data Summaries
```{r}
Original_Data%>%
  filter(Sodium.missing.flag == "Yes")%>%
  arrange(Age..Unit.Entry.)
```


### Sodium Data Table
```{r}
Sodium_Data <- Original_Data %>%
  select(Sodium ,Sodium.missing.flag, Age..Unit.Entry.)%>%
  mutate(Levels = case_when(
    between(Sodium, 112, 134.99) ~ "Low",
    between(Sodium, 135, 145.0) ~ "Normal",
    between(Sodium, 145.1, 165) ~ "High"))
Sodium_Data
```

## What does “missing sodium” represent – how is the data “managed”?
```{r}
Sodium_Data%>%
  filter(Sodium.missing.flag == "Yes")
```
Missing sodium means when the patient has enough sodium in their body to show they did not set off a test that could mean they are critically ill. 



# Data Visualization

Create a histogram for all Sodium data points

```{r}
Sodium_Data %>%
  ggplot() + 
  geom_histogram(aes( x = Sodium), binwidth = 1, fill = "Purple4") +
  labs(title = "Sodium Point (Including missing) levels in Tampa Patients")

```

# Sodium Level Histogram

```{r}
Sodium_levels <- Sodium_Data %>%
  filter(Sodium.missing.flag == "No")%>%
  ggplot() + 
  geom_histogram(aes(x = Sodium, fill = Levels), binwidth = .75)+
  labs(title=" All Available Sodium Levels in Tampa Patients", x="Sodium", y="Count")

Sodium_levels
```
- When sodium levels in the blood are *lower* than 135 meq/l, it is a condition called Hyponatremia.
- Sodium levels *between* 135 and 145meq/l are within the normal range.
- When sodium levels in the blood are *higher* than 145 meq/l, it is a condition called Hypernatremia.

# What is the Median Age for each sodium level?

The median age for Low sodium levels in Tampa Patients is 67 years old.
```{r}
Sodium_levels <- Sodium_Data %>%
  filter(Sodium.missing.flag == "No")%>%
  filter(Levels == "Low")%>%
  mutate(
    median_Age_Low = median(Age..Unit.Entry.) 
  )
 Sodium_levels
```
The median age for normal sodium levels in Tampa is 67 years old.
```{r}
Sodium_levels <- Sodium_Data %>%
  filter(Sodium.missing.flag == "No")%>%
  filter(Levels == "Normal")%>%
  mutate(
    median_Age_Normal = median(Age..Unit.Entry.) 
  )
 Sodium_levels
```
The median age for High sodium levels in Tampa is 66 years old.
```{r}
Sodium_levels <- Sodium_Data %>%
  filter(Sodium.missing.flag == "No")%>%
  filter(Levels == "High")%>%
  mutate(
    median_Age_High = median(Age..Unit.Entry.) 
  )
Sodium_levels
```



