---
title: "HSV Data Table"
output: html_document
Name: Arianna Pierre, Jenna Polur
---

```{r}
library(tidyverse)
```

#We will explore the Health Systems Engineering Dataset:

```{r}
Original_Data <- read.csv("HSE_Data.csv")
Original_Data
```
```{r}
view(Original_Data)
```

Reshaping the Data ?

#Data Summaries

#Create Sodium Data Table
```{r}
Sodium_Data <- Original_Data %>%
select(Sodium,Sodium.missing.flag)
Sodium_Data
```
#What does “missing sodium” represent – how is the data “managed”?
```{r}
Sodium_Data%>%
  filter(Sodium.missing.flag == "Yes")
```


```
```{r}
Sodium_count <- Sodium_Data%>%
  count("Sodium")
Sodium_count
```



#Data Visualization

Create a histogram for all Sodium data points
```{r}
Sodium_Data %>%
  ggplot() + 
  geom_histogram(aes(x= Sodium_count))
```



# Create histogram with bins that accurately group low, normal and high sodium
```{r}
Sodium_Data %>% 
ggplot () +
geom_histogram(aes(hist))
```

#Recreate histogram using chart including second axis for cumulative distribution



#Create pivot table with the sodium row and values
```{r}
library(pivottabler)
```


```{r}
git remote add origin https://github.com/jpolur/HSVNOTEBOOK.git

```


#Change name for X axis to low normal high
```{r}

```



